A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor interactions with proteins and DNA

### 2024-08-08 index.qmd
update some links (manuscript references still missing)

@@

@@

>>>>

You can interactively explore IP-MS and ChIP-seq data using `TFexplorer` at:
[https://data.fmi.ch/TFexplorer/](https://data.fmi.ch/TFexplorer/)

@@

Raw and processed data generated as part of this study is available from:

- **IP-MS data (PRIDE)**: [https://www.ebi.ac.uk/pride/archive/projects/PXD054070](https://www.ebi.ac.uk/pride/archive/projects/PXD054070)
- **RNA-seq data (GEO)**: [https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE274238](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE274238)
- **ChIP-seq data (GEO)**: [https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE274240](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE274240)

@@

The accompanying manuscript is available at:

- bioRxiv
- ...
